[DRAFT] - Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data

### 2015-11-23 paper01/paper.tex
Added new figures and paper was organized

\usepackage{graphicx} % for \includegraphics[scale=•]{•}

\begin{document}
\title{Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data}

@@

\subsection{Pattern Recognition}
\subsection{Situation Assesment}

@@

\subsection{Dataset}
 The dataset used for this work was provided by POSS research group and was used for \cite{Zhao2009}. The dataset consist of ten minutes of laser scanner raw data from six sensors arranged horizontally over an intersection near Peking University. Background model and calibration data for each laser scanner is also provided. Additionally, dataset contains trajectory info of objects in the scene, generated by their algorithm.

@@

As mentioned before, the dataset provides a background model for each laser scanner. This model was generated using a histogram of each sampling angle of scanning, then a peak is found indicating a motionless object, considered as background. With the peak values at all sampling angles the background model is obtained. Now, when a new frame comes from the laser scanner, the measure at certain angle is compared with the peak value associated with that angle. If the difference is larger than a given threshold, the measured value is considered to belong to a moving object at the intersection.

@@

With the set of points marked as foreground, clustering is performed to identify the set of points belonging to the same object. The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise. This algorithm does not need an estimated number of clusters as input, instead of this, it requires only two parameters: a minimum number of points per cluster, m, and a neighbourhood measure, $\epsilon$. A detailed description of the algorithm, can be found in \cite{Ester96}.
\subsection{Pattern Recognition}
\subsection{Situation Assesment}

@@

>>>>

\usepackage[pdftex]{graphicx} % for \includegraphics[scale=•]{•}
\usepackage{color}

\begin{document}
\title{[DRAFT] - Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data}

@@

\subsection{Pattern Recognition}

-TODO-

\subsection{Situation Assesment}

-TODO-

@@

\subsection{Dataset}
 The dataset used for this work was provided by POSS research group and was used for \cite{Zhao2009}. The dataset consist of ten minutes of laser scanner raw data from six sensors arranged horizontally over an intersection near Peking University. Background model and calibration data for each laser scanner is also provided. Additionally, dataset contains trajectory info of objects in the scene, generated by their algorithm. Figure \ref{inter_cfg} show intersection scenario, indicating position and orientation of each laser scanner inlcuded in dataset.

\begin{figure}[ht!]
\centering

\input{fig/intersection_config.tex}
\caption{System setup}
\label{inter_cfg}
\end{figure}

@@

As mentioned before, the dataset provides a background model for each laser scanner. This model was generated using a histogram of each sampling angle of scanning, then a peak is found indicating a motionless object, considered as background. With the peak values at all sampling angles the background model is obtained. Now, when a new frame comes from the laser scanner, the measure at certain angle is compared with the peak value associated with that angle. If the difference is larger than a given threshold, the measured value is considered to belong to a moving object at the intersection. In figure \ref{bg_proc} is described the background removal process.

\begin{figure}[ht!]
\centering

\input{fig/bg_process.tex}
\caption{Example of background removal applied to frame 123 from laser scanner 2 of dataset. In the upper plot, the raw data from the laser scanner is depicted. In the lower plot, red points represent the background model estimated based on peak values of the histogram. Black points are those marked as foreground after comparison of raw data with background data. The threshold used was 20. (Axis in centimeters).}
\label{bg_proc}
\end{figure}

@@

With the set of points marked as foreground, clustering is performed to identify the set of points belonging to the same object. The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise. This algorithm does not need an estimated number of clusters as input, instead of this, it requires only two parameters: a minimum number of points per cluster, m, and a neighbourhood measure, $\epsilon$. A detailed description of the algorithm, can be found in \cite{Ester96}.

\subsection{Pattern Recognition}

-TODO-

\subsection{Situation Assesment}

-TODO-

@@

-TODO-
